---
title: "Project 3: STAT302project3 Tutorial"
author: "Leqi Wang & Oscar Bai"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 3: STAT302project3 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This package includes 4 functions: `my_t.test`, `my_lm`, `my_knn_cv` and `my_rf_cv`, which are either for prediction or inference. First, we install the package from github and load the package using 'library()'.

```{r, eval = FALSE}
devtools::install_github("wang-leqi/STAT302proj3", build_vignette = TRUE, build_opts = c())
```
```{r, message = F}
library(STAT302proj3)
```

# Tutorial for my_t.test
```{r}
#A tutorial for my_t.test
#hypothesis: mean of the life Expectancy from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy data from my_gapminder does not equal to 60
my_t_test(x=(my_gapminder$lifeExp),alternative="two sided",mu = 60)

#hypothesis: mean of the life Expectancy data from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy data from my_gapminder is larger than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="greater",mu = 60)

#hypothesis: mean of the life Expectancy from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy from my_gapminder is smaller than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="less",mu = 60)

```
For the first t-test, we observe P = 0.09322877. Thus we have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is not equal to 60.

For the third t-test, we observe P = 0.04661438. Thus we  have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is greater than 60.

For the second t-test, we observe P = 0.9533856 Thus  we do not have sufficient evidence to reject the null hypothesis. Therefore, we cannot conclude that the real mean life expectancy is smaller than 60.

# Tutorial for my_lm
```{r}
#tutorial for my_lm
#Generate a regression using life Expectancy as your response variable and gdp Percaption and continent as explanatory variables
lm_fit <- my_lm(lifeExp ~gdpPercap + continent, data = my_gapminder)

#Write the hypothesis test associated with the gdpPercap coefficient.
my_t_test(x= my_gapminder$gdpPercap, alternative="less", mu = 4.452704e-04)

#predict the fitted values 
my_estimate <- lm_fit$Estimate
matrix <- model.matrix(lifeExp ~gdpPercap + continent, data = my_gapminder)
y_hat <- matrix %*% as.matrix(my_estimate)
df <- data.frame("actual" = my_gapminder$lifeExp, "fitted" = y_hat, "continent" = my_gapminder$continent)
#plot the Actual against Fitted values.
library(ggplot2)
x <- my_gapminder$gdpPercap
y <- df$y_hat
fitting_plot <- ggplot(df, aes(x=x, y=y, color = continent)) +
        ggtitle(label = "Actual vs Fitted Values") +
        geom_point(aes(x = actual, y = fitted)) +
        xlab(label = "Actual value") +
        ylab(label = "Fitted value") +
        geom_abline(slope = 1, intercept = 0) +
        theme_bw() 
        # geom_line(aes(x = x, y = fitted, col="Fitted value",lwd = 0.1)) 
        # labs(subtitle = paste("Testing Error:", round(test_err_k, 3))) +
        # theme_bw()
fitting_plot
```
1. interpret the gdpPercap coefficient: 
The coefficient of gdpPercap is 4.452704e-04 which means that for every one unit of increase in gdp Per capital, life Expectancy will increase 4.452704e-04.
2. interpret the results:
the gdpPercap hypothesis test using a p-value cut-off of a = 0.05.
p-value is 3.017639e-161 is significantly smaller than 0.05.Thus, we have enough evidence to reject that the null hypothesis that the mu of gdpPerCap is 4.452704e-04.
3.Interpret the Actual vs. Fitted values plot:
The model is not optimal. As the x-axis represents the actual lines, and the y axis represents the fitted value. The slope of the line would represent the percent of precision of the fitted value to the actual values. Here, the slope of the graph does not appear to be straight, which means that this model fit is not optimal.

# Tutorial for my_knn_cv
# Tutorial for my_rf_cv
