---
title: "Project 3: STAT302project3 Tutorial"
author: "Leqi Wang & Oscar Bai"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 3: STAT302project3 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

This package includes 4 functions: `my_t.test`, `my_lm`, `my_knn_cv` and `my_rf_cv`, which are either for prediction or inference. First, we install the package from github and load the package using 'library()'.

```{r, eval = FALSE}
devtools::install_github("wang-leqi/STAT302proj3", build_vignette = TRUE, build_opts = c())
```
```{r, message = F}
library(STAT302proj3)
```

# Tutorial for my_t.test
```{r}
#A tutorial for my_t.test
#hypothesis: mean of the life Expectancy from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy data from my_gapminder does not equal to 60
my_t_test(x=(my_gapminder$lifeExp),alternative="two sided",mu = 60)

#hypothesis: mean of the life Expectancy data from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy data from my_gapminder is larger than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="greater",mu = 60)

#hypothesis: mean of the life Expectancy from my_gapminder equals to 60(p-value cut-off of α=0.05)
#alternative hypothesis: mean of the life Expectancy from my_gapminder is smaller than 60
my_t_test(x=(my_gapminder$lifeExp),alternative="less",mu = 60)

```
For the first t-test, we observe P = 0.09322877. Thus we have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is not equal to 60.

For the third t-test, we observe P = 0.04661438. Thus we  have sufficient evidence to reject the null hypothesis and conclude that the true mean life expectancy is greater than 60.

For the second t-test, we observe P = 0.9533856 Thus  we do not have sufficient evidence to reject the null hypothesis. Therefore, we cannot conclude that the real mean life expectancy is smaller than 60.

# Tutorial for my_lm
# Tutorial for my_knn_cv
# Tutorial for my_rf_cv
